Appendix

### 2025-03-14 manuscript_rmarkdown/manuscript_appendix.Rmd
Test works (technically)
However, alpha has been defined the wrong way around?

\begin{definition}[Empirical central normality test]
$\mathcal{H}_0: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j = 0$

$\mathcal{H}_1: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j > 0$
\end{definition}

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\text{ecn},\alpha, n}$ for
empirical central normality at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The presented values should be divided by $100$.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

>>>>

\begin{definition}[Empirical central normality test]
The null-hypothesis is defined as: $\mathcal{H}_0: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j = 0$

THe alternative hypothesis is defined as: $\mathcal{H}_1: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j > 0$
\end{definition}

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\text{ecn},\alpha, n, \kappa = 0.70}$ for
empirical central normality at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}
